Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-15 draft.tex
Fixed 2 typos

The first literature to address unrecognized states directly was grounded in comparative politics, and a robust area-studies literature exists around each of the current cases of unrecognized statehood.\footnote{Lynch (2004), King (2001), Stanislawski (2008), and Bakke et al. (2013) provide notable treatments of the Former Soviet cases, and a pair of edited volumes by Bahcheli, Bartmann, and Srebrnik (2004) and Kingston and Spears (2004) each compile broader sets of case studies.} More recent literature has addressed wider ranges of cases and made important conceptual progress identifying patterns and commonalities across cases (e.g. Pegg 1998; Kolst\o \ 2006; Geldenhuys 2009; Caspersen and Stansfield 2011; Caspersen 2013). Bakke (2011) summarizes four primary explanations for the persistence of unrecognized states, each of which plays a role in the theory we develop here. Fist, economic and political elites often benefit from the status quo (e.g. King 2001). Second, the secessionists have sufficient military capacity to make military reconquest costly (e.g. Kolst\o \ 2006). Third, secessionists often enjoy external support from a patron (e.g. Lynch 2002; Stanislawski 2008. Lastly, the governments of unrecognized states are often internally legitimate, enjoying support from residents of the unrecognized state (e.g. Lynch 2002, Kolst\o \ 2006).

>>>>

The first literature to address unrecognized states directly was grounded in comparative politics, and a robust area-studies literature exists around each of the current cases of unrecognized statehood.\footnote{Lynch (2004), King (2001), Stanislawski (2008), and Bakke et al. (2013) provide notable treatments of the Former Soviet cases, and a pair of edited volumes by Bahcheli, Bartmann, and Srebrnik (2004) and Kingston and Spears (2004) each compile broader sets of case studies.} More recent literature has addressed wider ranges of cases and made important conceptual progress identifying patterns and commonalities across cases (e.g. Pegg 1998; Kolst\o \ 2006; Geldenhuys 2009; Caspersen and Stansfield 2011; Caspersen 2013). Bakke (2011) summarizes four explanations for the persistence of unrecognized states, each of which plays a role in the theory we develop here. First, economic and political elites benefit from the status quo (e.g. King 2001). Second, the secessionists have sufficient military capacity to make military reconquest costly (e.g. Kolst\o \ 2006). Third, secessionists enjoy external support from a patron (e.g. Lynch 2002; Stanislawski 2008. Lastly, the governments of unrecognized states are internally legitimate, enjoying support from residents of the unrecognized state (e.g. Lynch 2002, Kolst\o \ 2006).
